% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  
      \experience
    {January 2023}   {Senior Software Systems Engineer}{Nyeova Systems}{Parker, CO - USA}
    {May 2020} {
                      \begin{itemize}
                         \item	Lead Engineer in modelling and implementing an application for online food delivery and shop management built with React-Native, ReactJS and Electron with over 200+ clients.
                         \item Lead Engineer in modelling and implementing a contractor-based contact management system.
			\item Lead mobile frontend engineer.
			\item Architect and designed company's project codebases and models making it 95\% easier to understand by developers and non-developers.
			\item Constructed a more efficient and easy-to-understand scalable codebases with a 40\% increase in productivity.
			\item Designed and co-ordinated with teammates in setting up company's website and product's websites.
			\item Guided and supported 3 trainees in honing their skills.
			\item Created the developers workflow for a more efficient work environment.
			\item Architected company’s servers on Linode and Google Cloud making deployment seamless with 0\% human interaction.
			\item Provided time-saving and effective insights and feedback on company's workflows, projects and models, achieving a 56\% reduction in preparation of the software.
			\item Converted RestAPI to super optimised GraphQL APIs with an average response time of 86ms for 27, 625 http requests by 50 virtual users all in span of 12min 30s.
			\item Setup company's payment gateways.
		    \end{itemize}
                    }
                    {Typescript, Javascript, MySQL, Redis, ReactJS, React-Native, NextJS, GraphQL, RestAPIs, Linode VPS, Google Cloud, Docker, Nginx, Netlify, Bash Scripting, Python, Teams, Visual Studio Code, SCRUM}
  \emptySeparator
  
      \experience
    {January 2023}   {Senior Full-stack Developer}{JLS Trading Co.}{Charlotte, NC - USA}
    {November 2020} {
                      \begin{itemize}
			\item Collaborated with teammates to work on an amazon-based Inventory management system which can handle over more than a million products.
			\item Integrated amazon advertising APIs into our systems.
			\item Influenced 2 trainees to improve and get promoted to full-time working developers.
			\item Came up with cost efficient algorithms which saved us 96.67\% of the cost on Google cloud.
			\item Setup company’s DevOps and cloud based systems making deployment seamless with 0\% human interaction.
		    \end{itemize}
                    }
                    {Typescript, Javascript, MySQL, ReactJS, RestAPIs, Google Cloud, Docker, Bash Scripting, Python, Teams, Visual Studio Code}
  \emptySeparator

  
  \experience
    {October 2020}   {Backend Developer}{Asqii LLC}{Ghana}
    {September 2019} {
                      \begin{itemize}
                        \item Assisted my colleague with the development and maintenance of SchoolDesk.
                        \item Developed the backend for an asset management system.
                        \item Implemented an examination room assignment system for KNUST with over more than 40,000 students.
                      \end{itemize}
                    }
                    {Typescript, Javascript, MySQL, Slack, ReactJS, React-Native, Python, Flask, Pycharm, Visual Studio Code}
  \emptySeparator
  
  
    \experience
    {September 2020}   {Teaching Assistant | National Service Secretariat}{Kwame Nkrumah University of Science and Technology}{Ghana}
    {September 2019} {
                      \begin{itemize}
                        \item Assisted lecturers in the following courses; C programming, Classical Control Systems, Software Engineering 1 and 2, Basic Electronics.
                        \item Marking quizzes, lab reports, assignments and preparing continuous assessment for students.
                        \item Organised tutorial sessions to help students have a deeper understanding of the course.
                      \end{itemize}
                    }
                    {Typescript, Javascript, Python, Flask, MySQL, ReactJS, React-Native, Pycharm, Visual Studio Code, Slack}
  \emptySeparator
  
  
  
    \experience
    {December 2019} {Freelance Full-stack Developer }{\link{http://www.cafat.nc}{MITWORKS}}{Ghana}
    {March 2019}    {
                      \begin{itemize}
                        \item Implemented a full-stack mobile application, Votebook; A voting based mobile application.
                      \end{itemize}
                    }
                    {Typescript, Javascript, React-Native, NodeJS, MySQL, Visual Studio Code}
  \emptySeparator
  
  
  
  \experience
    {January 2020}     {Freelance Full-stack Developer}{Remotech LLC}{Ghana}
    {December 2019}    {
                      \begin{itemize}
                        \item Developed a full-stack mobile application, Automote; An IoT based mobile application for controlling the lightening system of homes, offices and street lights.
                      \end{itemize}
                    }
                    {Typescript, Javascript, React-Native, NodeJS, MySQL, Visual Studio Code}
  \emptySeparator
  
  
  
   \experience
    {August 2019}     {Full-stack Developer}{Millennium Promise Alliance}{Ghana}
    {January 2019}    {
                      \begin{itemize}
                        \item Implemented the back-end service for a software called RDLS which helped midwives to contact laboratories and send samples to request a lab test.
                        
                        \item Developed the mobile app for {
                        \link{https://play.google.com/store/apps/details?id=com.rdls&hl=en}{cRDLS}}.
                      \end{itemize}
                    }
                    {Typescript, Javascript, React-Native, NodeJS, MySQL, Python, Flask, Visual Studio Code, Pycharm}
  \emptySeparator
 
 
  \experience
    {August 2018}     {Backend Developer | Intern}{Asqii LLC}{Ghana}
    {June 2018}    {
                      \begin{itemize}
                        \item Conducted maintenance and code reviews on SchoolDesk application.
                        
                        \item Quality Assurance testing.
                        
                        \item Assisted the company in marketing the SchoolDesk Application to 20 different schools.
                      \end{itemize}
                    }
                    {MySQL, Python, Flask, Pycharm}
  \emptySeparator
  
    \experience
    {August 2017}     {Backend Developer | Intern}{Appatech Research Ghana }{Ghana}
    {June 2017}    {
                      \begin{itemize}
                        \item Code maintenance and debugging.
                        
                        \item Worked together with my colleagues in resolving bugs and issues.
                      \end{itemize}
                    }
                    { MySQL, Python, Django, Pycharm}
  \emptySeparator
\end{experiences}
