% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projects}{\faLaptop}

\begin{projects}

	\project
	{PigeonUltra}{2020 - 2021}
	{\website{https://pigeonultra.com}{Website} \googlePlay{https://play.google.com/store/apps/details?id=com.nyeova.pigeonbolt.client}{Playstore} \appStore{https://apps.apple.com/gh/app/pigeonbolt/id1546397948}{AppStore} \googlePlay{https://play.google.com/store/apps/details?id=com.nyeova.pigeonbolt.courier}{Playstore - Driver's version} \appStore{https://apps.apple.com/gh/app/pigeonbolt-courier/id1547093544}{AppStore - Driver's version} }
	{PigeonUltra is a mobile and online product that delivers quality e-commerce essentials from restaurants, groceries, bakeries, marketplace shops, and pet-care services in Ghana, West Africa.}
	{Typescript, Javascript, NodeJS, ReactJS, Python, Bash Scripting}

	\project
	{Omniscio}{2020 - 2021}
	{\website{https://app.omniscio.com}{Website}}
	{An amazon inventory management system.}
	{Typescript, Javascript, NodeJS, ReactJS, Python, Bash Scripting}

	\project
	{Project Blackbook}{2020}
	{\googlePlay{https://play.google.com/store/apps/details?id=com.nyeova.projectaid.blackbook}{Playstore}}
	{A contractor-based contact application for finding the right contractors for the right job.}
	{Dart, Flutter, Python, Flask}
	
	\project
	{SchoolDesk}{2018 - 2020}
	{\website{https://schooldesk.cc}{Website}}
	{A school management software with accounting capabilities and timetable generation feature.}
	{Typescript, Javascript, React-Native, NodeJS, ReactJS, Python, Flask}
	
	\project
	{iDoc}{2019 - 2020}
	{\website{https://idoc4u.com}{ https://idoc4u.com} \googlePlay{https://play.google.com/store/apps/details?id=com.arkdevs.jaatech.idoc}{Playstore}}
	{This project is to help clients to easily access and communicate with their doctors without the need of always going to the hospital. Project currently has 150+ clients and 10 doctors.}
	{Typescript, Javascript, React-Native, NodeJS, ReactJS}
				
	\project
	{Votebook}{2019 - 2020}
	{\googlePlay{https://play.google.com/store/apps/details?id=com.mitworks.votebook}{Playstore}}
	{A generic voting based mobile application.}
	{Typescript, Javascript, React-Native, NodeJS}
	
	
	\project
	{Automote}{2019 - 2020}
	{\googlePlay{https://play.google.com/store/apps/details?id=com.remotech.automote}{Playstore}}
	{An IoT based mobile application for controlling the lightening system of homes, offices and street lights effortlessly. This helped save 70\% of the power consumed on the KNUST campus as power could be scheduled when to come on or off.}
	{Typescript, Javascript, React-Native, NodeJS}
	
	\project
	{Project Aquanaut}{2018 - 2019}
	{\github{aquanautpro/aquanaut-community} \website{https://aquanaut.netlify.com}{ Final Year Project, KNUST}}
	{A Data Analytics Platform and sensor node for leakage detection and management in water distribution networks.}
	{Typescript, Javascript, NodeJS, ReactJS, Python, Flask}
	
	\project
	{Erranda App}{2018 - 2019}
	{\gitlab{ACESIV/back-end/errand-boy-main-backend} \website{https://gitlab.com/ACESIV/back-end/errand-boy-main-backend}{ Software Engineering II, KNUST}}
	{This project presents a system that allows users post errands they want to be run so errand guys can bid and run the errands for a fee.}
	{Typescript, Javascript, Python, Flask, React-Native, ReactJS}
	
	\project
	{CodeForMe}{2018}
	{\github{Silvrash/codeForMe} \website{https://codeforme.herokuapp.com/}{ Artificial Intelligence Project, KNUST}}
	{This project used AI to convert speech to python code. (Natural language to code platform using semantic parsing and artificial neural networks).}
	{Typescript, Javascript, ReactJS, Python, Tensorflow, Flask}
	
	\project
	{BookIT}{2017}
	{\gitlab{facta01/BookIT} \website{https://gitlab.com/facta01/BookIT}{ Software Engineering Project, KNUST}}
	{This project helps students to book buses to convey them to their destinations during school breaks and vacations.}
	{Java Android, Python, Flask}
	
	\project
	{Egg Collector}{2017}
	{\gitlab{benjin/egg-collector} \website{https://gilab.com/benjin/egg-collector}{ Exchange Program Project, KNUST}}
	{A computer vision-based project for egg detection and determining if an egg is viable or not, grouping the eggs into those which are good and the spoilt ones.}
	{Python, Arduino}
\pagebreak

	\project
	{MovX}{2016}
	{\gitlab{benjin/movx-android} \website{https://gitlab.com/benjin/movx-android}{Personal Project}}
	{A mobile application for keeping track of movies, reading and viewing latest trends of manga.}
	{Python, Java Android, Flask}

\end{projects}
